\documentclass{article}

\title{Mixing Demo}
\author{Alexei Ozerov}
\date{December, 18th/2017}

\begin{document}

\maketitle
\tableofcontents

\section{Introduction}

Brian Martin will demo the mixing (in the box) of three student tunes.

\subsection{The Approach}

The Truth (in 2017):

\medskip

\begin{itemize}
\item Melody, Harmony, Rhythm - Europe (Art)
\item Rhythm, Melody, Harmony - Africa (Practical)
\item Melody + Rhythm - Current
\item The mix \textbf{must have melody + rhythm}. Don't screw up the groove, don't mess up the vocal.
\item If the mix doesn't make you move, if you have to think, it is not working.
\item Engage people viscerally - then add harmony, etc.
\end{itemize}

\medskip

Art is \textbf{expression}.

\medskip

Get your \textbf{ego} out of the mix.

\medskip

Everything you do has a price, and minimalism is something to do.

\medskip

Try pulling the faders down \& removing plugins, and building up the mix from the beginning, and re-engage with the mix.

\section{Song \#1: Chris}

\begin{itemize}
\item Begins by setting up the balance of the drums
\item DI is a waste of time
\item Avoid using ``solo'' - the interrelationships of sounds is what makes the mix
\item Mixes relatively quietly 
\item Overheads, Kick, Snare (all you need for the drums)
\item Reverb+Delay panned right if mono original is left 
\item Avoid stereo everywhere - phase issues,etc.
\item Uses ``Echo Boy''
\item Label your I/O in the I/O preferences section 
\item Take the time to set your mix up
\item When creating Stereo with delay, don't put it in the middle, because you'll get into the vocals and the groove
\item 2mt2140 Reverb
\item Dip at 40Hz in the overheads 
\item Save with iterations when mixing
\item \textbf{``Fab Filter's aiight ...''}
\item Use your ears when you mix - close your eyes!
\item Careful with compression, don't worry about attack speed unless you have sibalencec problems
\item Tune your drums!!
\item Dip at 20Hz on kick drum 
\item Another ``penis region'' ... ``if you boost before 40Hz, it is about your dick''
\item Bass better through AMP because of bad low frequency reproduction
\item Greg Calbi
\item Take out BUT put back ... find the voice a little above and return it with very narrow Q values
\item Wide stereo delay print to create a ``back wall''
\item Careful with compression - can create vocal sub compression bus
\item Make the least number of choices possible - make them all before you record, or as you record
\item Fix a problem with EQ, and then work with compression, as there may be issues with how the compressor responds to the changes in EQ
\end{itemize}

\medskip

Fuck the Bus Compressor, because apparently bus compressor = sexual inadequecy. 100\%.

\medskip

LA2A Thing



\end{document}
