\documentclass{article}

\author{Alexei Ozerov}
\date{}
\title{Recording Techniques Class \#1 - Post Strike \#1}

\begin{document}

\maketitle

\tableofcontents

\begin{center}
\noindent\rule{14cm}{0.4pt}
\end{center}

\pagebreak

\section{Class Introduction}

\subsection{Strike}

There will be a test about the Union.

\medskip

You need to know:

\medskip

\begin{enumerate}
\item Head of negotiating
\item Pro Tools Workshop
\item Shorter Midterm + Pro Tools Workshop
\end{enumerate}

\section{DIs}

\subsection{Why}

\begin{itemize}
\item Consistent Level
\item Phantom Power
\item Balanced Output
\item Guitars Have Unbalanced Output
\item Isolation
\item Clearer Transients
\item Record Both Mic and DI
\end{itemize}

\subsection{Features \& Mechanics}

You can record direct by plugging into INPUT, and then sending the OUTPUT as an XLR. The box converts instrument level to microphone level. Balances the signal before the console gets it. The THROUGH lets you send the signal to the AMP as well if you want to record that. The DI splits the signal into two outputs. One goes to the mic input on the console, and the other goes to the amp. 

\medskip

The DI Box:

\medskip

Instrument Output: Unbalanced, high Impedance, Instrument Level

\medskip

Console or Interface: Balanced, Low Impedance, Mic Level Signal

\subsection{Passive DI}

Simplest Design, which uses a transformer to convert impedance (high to low), and balance the signal. The Passive DI has a magnet inside it with PRIMARY and SECONDARY windings. Has a STEP DOWN TRANSFORMER, which gelps get rid of noise.

\medskip

RADIAL JDI

\medskip

Some interesting things you can do with passive DIs is make long cable runs. Using two passive DIs:

\medskip

INPUT - PATCHBAY - INTO XLR OUTPUT - INPUT WORKS AS OUTPUT INTO AMP. 

\medskip

Another thing one can do is REAMP with passive DIs. One gets a dry signal from the DI, and later on, you send the signal from the console (XLR), and send it back into an amp, and record the amp. This was, you can get a better tone. Has benifits encompasing space, noise, etc.

\medskip

DIs can be a little strange when listening to yourself as you play, as the dry signal provided would sound pretty lame.

\subsection{Active DI}

Must provide power for this to work.











\end{document}
